Independent discovery of a nulling pulsar with unusual sub-pulse drifting properties with the Murchison Widefield Array

### 2022-03-01 paper/referee_report_1/response.md

7. Please indicate the flux value in the ordinates of Figure 1 for each averaged pulse profiles.

  * Since we do not have reliable absolute fluxes at this stage, Figure 1 shows normalised profiles. We have added "peak-normalised" to the caption of the figure.

8. It is difficult to determine whether nulling or just weak emission exists in this pulsar only from Figures 2 and 3. The pulse energy distribution is a statistical way to characterize the nulling behavior (Wen et al. 2020, ApJ, 904, 72).

  * We have now included pulse energy distributions for all six observations (see also our response to points 12 & 13 below). From the distributions of the two 20-min observations in which the pulsar was not detected in a periodicity search, we conclude that if there is any weak emission, it must fall far below the MWA's detection threshold. The new text discussing the pulse energy histograms can be found in Section 3.1.

### 2022-03-01 paper/main.tex
Added a response to the referee comment about pulse energy distributions

This working definition of a null may misclassify pulses with broad emission spread out over the pulse window, even if its integrated flux density is statistically significant.
{\bf For comparison, we present the pulse energy histograms of both on- and off-pulse regions of the pulse stacks for each of the six observations in Fig. \ref{fig:nullhist}.
The similarity between the on- and off pulse distributions for observations 1275094456 and 1275172216 indicate that any broad emission that is present falls well below the MWA detection threshold, and therefore that the detection of single pulses as described above is in this case is a more robust method for measuring the nulling fraction.
Despite this}, the uncertainty in our estimate of the nulling fraction will still be dominated by the lack of a statistically significant number of burst sequences.

>>>>

This working definition of a null may misclassify pulses with broad emission spread out over the pulse window, even if its integrated flux density is statistically significant.
{\bf For comparison, we present the pulse energy histograms of both on- and off-pulse regions of the pulse stacks for each of the six observations in Fig. \ref{fig:nullhist}.
The similarity between the on- and off pulse distributions for observations 1275094456 and 1275172216 indicate that any broad emission that is present falls well below the MWA detection threshold.
Despite this}, the uncertainty in our estimate of the nulling fraction will still be dominated by the lack of a statistically significant number of burst sequences.
